---
title: "group36"
author: "Ido Goldman, Amit Fedaeli and Amir Yativ"
date: "2023-01-02"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r libraries, include=TRUE,echo=TRUE}
library(fitdistrplus)
library(magrittr)
```
## Introduction
we divided this document into two parts : the first one analyzing the distribution for the couples, and the second one testing the couple’s distribution.

##couples first comparing
in this part we presenting the information for each distribution
```{r }
dataset <- read.csv(file.choose(), header = T)
couples <- (dataset$X1)
normFit <- fitdist(couples,"norm")
summary(normFit) 
expFit <- fitdist(couples,"exp")
summary(expFit)

```

## families first comparing

in this part we presenting the information for each distribution

```{r }
families <- (dataset$X2)
print(families)
expFit <- fitdist(families,"exp")
normFit<-fitdist(families,"norm") # fitting a normal distrbution 
summary(normFit)
summary(expFit)

```


##Comparing Plots
this section will show us which distribution is the correct one according to Q-Q and P-P plots, among distribution lines combined with theoretical data :

```{r pressure, echo=FALSE}

plotdist(families,"norm",para=list(mean=normFit$estimate[1], sd=normFit$estimate[2] ) )
plotdist(families,"exp",para=list(rate=expFit$estimate[1]))
plotdist(couples,"norm",para=list(mean=normFit$estimate[1], sd=normFit$estimate[2] ) )
plotdist(couples,"exp",para=list(rate=expFit$estimate[1]))


```

##combined compairing Plots
this section combine both lists in one table for better view and compare:


```{r pgenerate}
par(mfrow=c(2,2)) # manually define a 2X2 graph window 
legendText<-c("exp","norm") # define legend text
denscomp(list(expFit,normFit),legendtext=legendText) # 
qqcomp(list(expFit,normFit),legendtext=legendText)  # 
cdfcomp(list(expFit,normFit),legendtext=legendText) # 
ppcomp(list(expFit,normFit),legendtext=legendText) 

```
